\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-10-23 AffineLieAlgebras/InformalNotes/article.tex
Description of regular embeddings

\begin{document}
Plan:

@@

$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}\right) $ -- the set of singular weights $%
\xi \in P$ $\left( \text{resp. }\in P_{\frak{a}}\right) $ for the module $%
L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) $ with the
coordinates $\left( \overset{\circ }{\xi },k,n,\epsilon \left( w\left( \xi
\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
)-\rho },$ (resp. $\left( \overset{\circ }{\xi },k,n,\epsilon \left(
w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
\circ (\nu +\rho _{a})-\rho _{a}}$ ), (this set is similar to $P_{\mathrm{%
nice}}^{\prime }\left( \mu \right) $ in \cite{Wak1})

@@

\begin{comment}
  When such a subset does exist?  
\end{comment}

@@

\begin{comment}
  Prove it  
\end{comment}

@@

Let's denote the subalgebra with the root space spanned over the set $\Delta_{\bot}$ by $\mathfrak{a}_{\bot}$.
\begin{comment}
  Shouldn't we prove that such a subalgebra exists and is tractable?
\end{comment}
Then we see that
\begin{multline}
  \label{eq:14}
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}} =\\
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}=\\
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{\rho_{\mathfrak{a}_{\bot}}-\rho} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
\end{multline}
The projection $\pi_{\mathfrak{a}}$ of the character of the highest-weight module $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ is equal to the dimension of the module multiplied by $e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}})}$
  \begin{multline}
    \label{eq:15}
    \pi_{\mathfrak{a}}\left(\sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{\rho_{\mathfrak{a}_{\bot}}-\rho} ch L^{\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
    \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
  \end{multline}
These dimensions of the modules could be easily calculated using Weyl formula.

>>>>

\begin{document}
\title{\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}}
\author{Vladimir Lyakhovsky\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:lyakh1507@nm.ru \\
[5mm] Anton Nazarov \\
%EndAName
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:antonnaz@gmail.com\\
}
\maketitle

\begin{abstract}

\end{abstract}

@@

$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}\right) $ -- the set of singular weights $%
\xi \in P$ $\left( \text{resp. }\in P_{\frak{a}}\right) $ for the module $%
L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) $ with the
coordinates $\left( \overset{\circ }{\xi },k,n,\epsilon \left( w\left( \xi
\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
)-\rho },$ (resp. $\left( \overset{\circ }{\xi },k,n,\epsilon \left(
w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
\circ (\nu +\rho _{a})-\rho _{a}}$ ), (this set is similar to $P_{\mathrm{%
nice}}^{\prime }\left( \mu \right) $ in \cite{wakimoto2001idl})

@@

Let's denote the subalgebra with the root space spanned over the set $\Delta_{\bot}$ by $\mathfrak{a}_{\bot}$.

Now we should discuss when the subset $\Delta_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta_{\bot}$ is empty.
Then the modules $L_{\mathfrak{a}_{\bot}}$ are trivial, the dimensions are equal to 1 and we get the formula (11) from the paper \cite{ilyin812pbc}.

Non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained through the chain of maximal embeddings $\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$. Also the maximal regular embeddings are constructed by the exclusion of one or two roots from the extended Dynkin diagram of the algebra. Since this process can give us non-connected Dynkin diagrams we can see which roots are orthogonal to the root space of non-maximal regular subalgebra $\mathfrak{a}$.

Consider for example regular embedding of $A_1\subset B_2$ ($su(2)\subset so(5)$).

The extended Dynkin diagram of $B_2$ 
\begin{equation}
  \label{eq:8}
  \begin{diagram}
    \node{\circ}\arrow{e}{}\node{\circ}\arrow{e}{}\node{\circ}\\ \\
    \node{\circ}\node[2]{\circ}
  \end{diagram}
\end{equation}
We then drop central node and get the embedding $A_1\otimes A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
\begin{comment}
  Consider special embeddings
\end{comment}

@@

If the set $\Delta_{\bot}$ is non-empty then Weyl reflections corresponding to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.

We have denoted the subalgebra with the root space spanned over the set $\Delta_{\bot}$ by $\mathfrak{a}_{\bot}$.

@@

Then we see that
\begin{multline}
  \label{eq:14}
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}} =\\
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}=\\
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{\rho_{\mathfrak{a}_{\bot}}-\rho} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
\end{multline}
The projection $\pi_{\mathfrak{a}}$ of the character of the highest-weight module $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ is equal to the dimension of the module multiplied by $e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}})}$
  \begin{multline}
    \label{eq:15}
    \pi_{\mathfrak{a}}\left(\sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{\rho_{\mathfrak{a}_{\bot}}-\rho} ch L^{\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
    \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
  \end{multline}
These dimensions of the modules could be easily calculated using Weyl formula.
